\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-04-07 k-planar.tex
addedc omment re map graphs

% \note{DW}{I suggest we delete ``We use $G'\subseteq G$ to denote subgraph containment; that is, $V(G')\subseteq V(G)$ and $E(G')\subseteq E(G)$. '' This is absolutely standard.}

@@

% \note{DW}{Mention other application such as vertex ranking~\citep{BDJM}, twin-width~\citep{BKW}, odd colourings~\citep{DMO}? We write a lot about adjacency labellings and universal induced subgraphs. Do we need so much detail here? We also mention this work in \cref{WrappingUp}.}

% \note{PM}{Agreed. I cut this down to a list of famous open problem. We don't need to sell this so hard anymore.}

@@

%\note{DW}{Do we want to mention ``every $1$-planar graph is contained in $H\boxtimes P\boxtimes K_7$ for some planar graph $H$ of treewidth $3$ and for some path $P$'' here?}
%\note{PM}{Yes, I think so.  Two theorems, like this, or one?}
%\note{DW}{two theorems}

@@

% A planar graph of treewidth at most $3$ is said to have \emph{simple treewidth} $3$.

@@

% \note{DW}{I'm uncomfortable about saying that $k$-planar graphs are our most high-profile target. Why are they more important than map graphs or nearest neighbour graphs? I suggest ``
% The above result for $k$-planar graphs (\cref{kPlanarProduct}) is in fact a special case of a more general result that relies on the following definition. A non-empty set $\SS$  ....''}

@@

% \note{PM}{Suggested new Proof}
% \note{DW}{I am happy with the new proof, once we address the issues.}

@@

  Let $x$ be a vertex of $G_0$, let $F_x$ be the corresponding face of $G_0^*$, and let $v_1,\ldots,v_s$ be the facial cycle of $F_x$.  Let $C:=w_1,\ldots,w_r$ be the subsequence of $v_1,\ldots,v_s$ consisting of only the nation vertices.  Since $x$ is incident to at most $d$ nations, $r\le d$.
  Call $C_x$ the \defin{nation cycle} of $F_x$.

  \note{DW}{What if there are 1 or 2 nations incident to $x$? Is $C_x$ a cycle? Do we need parallel edges here?}

  \note{PM}{If $r=1$ then the ``nation cycle'' has no edges, so this doesn't contribute any edges to $G_1$, which is the right thing to do.}

  \note{PM}{If $r=2$ then the ``nation cycle'' has one edge, so this contributes one edge to $G_1$ (which is needed, because the corresponding nations are adjacent, but no other edges are needed.)}

  Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding each nation cycle of each face $F$ of $G_0$ and then triangulating each face with more than $d$ vertices on its boundary.  Each nation cycle is now a face of $G_1$ and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.

>>>>

@@

@@

@@

@@

@@

@@

  Let $x$ be a vertex of $G_0$, let $F_x$ be the corresponding face of $G_0^*$, and let $v_1,\ldots,v_s$ be the facial cycle of $F_x$.  Let $C:=w_1,\ldots,w_r$ be the subsequence of $v_1,\ldots,v_s$ consisting of only the nation vertices.  Since $x$ is incident to at most $d$ nations, $r\le d$. Call $C_x$ the \defin{nation cycle} of $F_x$. Note that if $r=1$ then the ``nation cycle'' has no edges, and if $r=2$ then the ``nation cycle'' has one edge. \note{DW}{Perhaps we shouldn't call it the ``nation cycle'' since it is not necessarily a cycle.}

  Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding the nation cycle of each face $F$ of $G_0$, and then triangulating each face with more than $d$ vertices on its boundary.  Each nation cycle \note{DW}{add `` of length at least 3''} is now a face of $G_1$, and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.
